Understanding Feedback Mechanisms in Machine Learning Jupyter Notebooks

### 2024-07-30 report/emse24.tex
feat(report): emse24 update t2v

>>>>

We enforced a time resource limit of 200 hours for conducting the case studies in RQ2 and RQ3, potentially constraining the depth and breadth of our investigation. The stratified random sampling used for selecting the case study candidates mitigates this threat by ensuring that a representative cross-section of the population is sampled within the time constraint. While this sampling method enhances the generalizability of our results, the time limitation should still be considered when interpreting and applying the study's findings.
